Empowering the use of preprints in ecology and evolution: an exploration of the first 1000 *EcoEvoRxiv* preprints

### 2023-10-15 ms/ms.qmd
Added code to check preprint duplicates

# Dates preprints were published, range and graph
  dates <- range(data$`Published Date`)
```

>>>>

# Check duplicate titles. Appears some folks submitted the same paper multiple times instead of simply updating their existing one.

  # First make sure there is no case sensitivity 
  data <- data %>% mutate(title = tolower(`Preprint Title`))

  # Check for duplicates
  dupl <-  data %>%
    group_by(title) %>% 
    summarise(n = n()) %>% 
    filter(n > 1)

  # Remove duplicates
    data <- data %>% 
            distinct(title, .keep_all = TRUE)

  # Check success. Should be 1216. Yes
    dupl <- data %>%
            group_by(title) %>% 
            summarise(n = n()) %>% 
            filter(n > 1)

# Dates preprints were published, range and graph
  dates <- range(data$`Published Date`)
